---
title: "a3_task3_elijah_baker.Rmd"
author: "E Baker"
date: "10/28/2021"
output: html_document
---
## Info

### Data citation

warnings and messages masked; everything else - code, outputs, text - should show up in your knitted document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Load packages
```{r}
library(tidyverse)
library(janitor)
library(here)
```


## Read data
```{r}
urchins <- read.csv(here("data", "urchins.csv"))

```

## Data visualization: Size comparsions between purple and red urchins
Section 1: Size comparisons, purple and red urchins (include data from all sites, and for both treatments - i.e. ignore those variables here)

Data visualization: compare the distribution of sizes between purple and red urchins with a finalized, faceted histogram. You will probably want to reduce the number of bins (default is 30...we recommend closer to 10 here). Finalize your graphs and add a figure caption.

```{r}
urchins_clean <- urchins %>%
  clean_names()

ggplot(data=urchins_clean, aes(x=size, fill=common_name)) +
  scale_fill_manual(values=c("#674ea7", "#900000")) + 
          geom_histogram(bins=10) +
  facet_wrap(~common_name) + 
  theme() +
  labs(x= "Number of sea urchins",
       y= "Diameter of sea urchins (cm)",
       title= "Comparisson of sea urchin diameter between red and purple urchins (BAKER)")

       
```





## FOR A TABLE--
  knitr:: kable(df) %>%
    kable_styling(...) [can google which styling to use to create a better table]



